DATA 621 Homework #4

### 2019-11-08 hw4/HW4.Rmd
added some predictions

test$Prediction2 =predict.glm(glm2, newdata=test, type="response")

glm3 <- glm(TARGET_AMT ~ AGE+PARENT1+MSTATUS+JOB+BLUEBOOK+TIF+CAR_AGE_density+URBANICITY+MVR_PTS+REVOKED+CLM_FREQ+OLDCLAIM , data= train, family=poisson) 
summary(glm3)

test$Prediction =predict.glm(glm3, newdata=test, type="response")

cor(test$TARGET_AMT, test$Prediction)
```

@@

>>>>

@@

test$Prediction2 =predict.glm(glm2, newdata=test, type="response",family=poisson)

cor(test$TARGET_AMT, test$Prediction2)

ggplot(test, aes(x=Prediction2, y=TARGET_AMT)) +
     geom_point(shape=1) +    # Use hollow circles
     geom_smooth()            # Add a loess smoothed fit curve with confidence region

glm3 <- glm(TARGET_AMT ~ AGE+PARENT1+MSTATUS+JOB+BLUEBOOK+TIF+CAR_AGE_density+URBANICITY+MVR_PTS+REVOKED , data= train, family=poisson) 
summary(glm3)

test$Prediction3 =predict.glm(glm3, newdata=test, type="response")

cor(test$TARGET_AMT, test$Prediction3)
```
